Structured Versus Decorated Cospans

### 2020-11-17 cospans.tex
Update cospans.tex

@@

@@

@@

@@

@@

@@

>>>>

\node (A) at (0,0) {$U_{\lH(a)} \odot \lH(M)$};
\node (B) at (2.5,0) {$\lH(U_a) \odot \lH(M)$};
\node (C) at (0,-1) {$\lH(M)$};
\node (D) at (2.5,-1) {$\lH(U_a \odot M)$};
\node (A') at (5,0) {$\lH(M) \odot U_{\lH(b)}$};
\node (B') at (7.5,0) {$\lH(M) \odot \lH(U_b)$};
\node (C') at (5,-1) {$\lH(M)$};
\node (D') at (7.5,-1) {$\lH(M \odot U_b)$};

@@

(A) edge node[above]{$\lH_U \odot 1$} (B)

@@

(B) edge node[right]{$\lH_{U_a,M}$} (D)
(D) edge node[above]{$\lH(\lambda')$} (C)
(A') edge node[above]{$1 \odot \lH_U$} (B')

@@

(B') edge node[right]{$\lH_{M,U_b}$} (D')
(D') edge node[above]{$\lH(\rho')$} (C');

@@

The diagrams involving the morphisms of decorations are similar to those in Theorem \cref{DC}. This shows that $\lH=(H,E,\theta)$ is a double functor. Next we show that this double functor is symmetric monoidal. First, that the object component $\lH_0=H$ is symmetric monoidal is clear as $H \maps \A \to \A'$ preserves finite colimits. As for the arrow component $\lH_1$, given two horizontal 1-cells $M_1$ and $M_2$ in $F\lCsp$:

@@

and the image of this horizontal 1-cell under the double functor $\lH$ is $\lH(M_1 \otimes M_2)$ given by:

@@

\node (D) at (2,-0.5) {$d_{\lH(M_1 \otimes M_2)} = \theta_{c_1+c_2} E(d_{M_1 \otimes M_2})\phi \in F'(H(c_1+c_2))$};
